ENME 625 \\ Multi-Objective Optimization with Genetic Algorithms

### 2017-05-06 draft1_SM.tex
added more content

\usepackage{color} %red, green, blue, yellow, cyan, magenta, black, white
\definecolor{mygreen}{RGB}{28,172,0} % color values Red, Green, Blue
\definecolor{mylilas}{RGB}{170,55,241}

@@

\noindent The next sections shall discuss the unconstrained problems ZDT1, ZDT2, and ZDT3, the results from the fitness function NSGA and MATLAB's "ga" function as well as the results from MATLAB's "gamultiobj" function for each.

\subsection{ZDT1} 
The first test problem, denoted as ZDT1 in \cite{deb2001multi} is shown below.

@@

\noindent The true Pareto frontier for this problem occurs when $x_i = 0$ for i = 2,...,30. Figure~\ref{fig:ZDT1} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. The quality metrics chosen to evaluate this problem are Coverage Difference (CD)and Pareto Spread (OS). Ten runs for each algorithm were performed and the mean and standard deviation of each metric are tabulated in Table~\ref{tab:ZDT1}.
\begin{figure}[h]
  \caption{Example Pareto Results for ZDT1}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT1_pareto_final.png}  
  \label{fig:ZDT1}
\end{figure}

@@

\subsection{ZDT2} 
The second test problem, denoted as ZDT2 in \cite{deb2001multi} is shown below.

@@

\noindent The true Pareto frontier for this problem, similar to ZDT1, occurs when $x_i$ = 0 for i = 2,...,30. Figure~\ref{fig:ZDT2} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. Table~\ref{tab:ZDT2} summarizes the mean quality metrics for each algorithm for ten runs.
\begin{figure}[h!]
  \caption{Example Pareto Results for ZDT2}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT2_pareto_final.png}  
  \label{fig:ZDT2}
\end{figure}

\begin{table}[h]
\caption{Quality Metrics for ZDT2} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.7832  (0.0821) & 0.6971  (0.0094) \\ \hline
OS &  0.8781 (0.0946) & 1.0086 (0.0278)  \\ \hline
\end{tabular}
\label{tab:ZDT2} 
\end{table}
\begin{figure}[h]
  \caption{ZDT2 Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT2_QM.png}  
  \label{fig:ZDT2_QM}
\end{figure}

\subsection{ZDT3} 
The third test problem, denoted as ZDT3 in \cite{deb2001multi} is shown below.

@@

\begin{figure}[h]
  \caption{Example Pareto Results for ZDT3}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT3_pareto_final.png}  
  \label{fig:ZDT3}
\end{figure}

\begin{table}[h]
\caption{Quality Metrics for ZDT3} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.7407 (0.0050) & 0.7554 (0.0031) \\ \hline
OS & 0.8565 (0.0098) & 0.8489 (0.0180) \\ \hline
\end{tabular}
\label{tab:ZDT3} 
\end{table}
\begin{figure}[h]
  \caption{ZDT3 Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT3_QM.png}  
  \label{fig:ZDT3_QM}
\end{figure}

@@

\begin{align*}
\textrm{Minimize} ~~~~~ f_1(\textbf{x}) &= -(25(x_1-2)^2+(x_2-2)^2+(x_3-1)^2+(x_4-4)^2+(x_5-1)^2) \\
\textrm{Minimize} ~~~~~ f_2(\textbf{x}) &= \sum_{i=1}^{6}x_i^2 \\
\textrm{Subject to} ~~~~ g_1(x) &= 1-\frac{x_1+x_2}{2} \leq 0 \\
g_2(x) &= \frac{x_1+x_2}{6}-1 \leq 0 \\
g_3(x) &= \frac{x_2-x_1}{2}-1 \leq 0 \\
g_4(x) &= \frac{x_1-3x_2}{2}-1 \leq 0 \\
g_5(x) &= \frac{(x_3-3)^2+x_4}{4}-1 \leq 0 \\
g_6(x) &= 1-\frac{(x_5-3)^2+x_6}{4} \leq 0 \\
0 &\leq  x_1,x_2,x_6  \leq 10 \\
1 &\leq  x_3,x_5  \leq 5 \\
0 &\leq  x_4  \leq 6 \\
\end{align*}
\begin{figure}[h]
  \caption{True Pareto Frontier for OSY}
  \centering
  \includegraphics[width=0.85\textwidth]{OSY_pareto_true.png}  
  \label{fig:OSY_true}
\end{figure}

@@

\begin{table}[h]
\caption{Quality Metrics for OSY} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.7882 (0.1995) & 0.5507 (0.0685)  \\ \hline
OS & 0.5322 (0.3393) & 0.9608 (0.2427) \\ \hline
\end{tabular}
\label{tab:OSY} 
\end{table}
\begin{figure}[h]
  \caption{OSY Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{OSY_QM.png}  
  \label{fig:OSY_QM}
\end{figure}

\subsection{TNK} 
This test problem, denoted as TNK in \cite{deb2001multi} is shown below with the true Pareto frontier shown in Figure~\ref{fig:TNK_true}.

\begin{align*}
\textrm{Minimize} ~~~~~ f_1(\textbf{x}) &= x_1 \\
\textrm{Minimize} ~~~~~ f_2(\textbf{x}) &= x_2 \\
\textrm{Subject to} ~~~~ g_1(x) &= -x_1^2-x_2^2+1+0.1\cos(16\arctan(\frac{x_1}{x_2})) \leq 0 \\
g_2(x) &= (x_1 - 0.5)^2 + (x_2 - 0.5)^2 -0.5 \leq 0 \\
0 &\leq  x_1,x_2 \leq \pi \\
\end{align*}
\begin{figure}[h]
  \caption{True Pareto Frontier for TNK}
  \centering
  \includegraphics[width=0.85\textwidth]{TNK_pareto_true.png}  
  \label{fig:TNK_true}
\end{figure}

@@

\begin{table}[h]
\caption{Quality Metrics for TNK} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD &  0.8581 (0.0480) & 0.7792 (0.0036) \\ \hline
OS & 0.4177 (0.3216) & 0.9763 (0.0178)\\ \hline
\end{tabular}
\label{tab:TNK} 
\end{table}
\begin{figure}[h]
  \caption{TNK Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{TNK_QM.png}  
  \label{fig:TNK_QM}
\end{figure}

\subsection{CTP} 
This test problem, denoted as CTP in \cite{deb2001multi} is shown below and the true Pareto frontier is shown in Figure~\ref{fig:CTP_true}.

\begin{align*}
\textrm{Minimize} ~~~~~ f_1(\textbf{x}) &= x_1 \\
\textrm{Minimize} ~~~~~ f_2(\textbf{x}) &= g(x)(1-\sqrt{\frac{f_1(x)}{g(x)}} \\
\textrm{Subject to} ~~~~ g_1(x) &= a|\sin(b\pi(\sin(\theta)(f_2(x)-e)+\cos(\theta)f_1(x))^c)|^d \\
&- \cos(\theta)(f_2(x)-e)-\sin(\theta)f_1(x) \leq 0 \\
\textrm{where} ~~~~~~~~~~ \theta &= -0.2\pi, a = 0.2, b=10, c=1, d=6, e = 1 \\
g(x) &= |1+(\sum_{i=2}^{10}x_i)^{0.25}| \\
0 &\leq  x_1  \leq 1 \\
-5 &\leq  x_i  \leq 5, i = 2,...,10 \\
\end{align*}
\begin{figure}[h]
  \caption{True Pareto Frontier for CTP}
  \centering
  \includegraphics[width=0.85\textwidth]{CTP_pareto_true.png}  
  \label{fig:CTP_true}
\end{figure}

@@

\begin{table}[h]
\caption{Quality Metrics for CTP} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.6802 (0.0067) &  0.6802 (0.0092) \\ \hline
OS & 0.7901 (0.0734) & 0.5959 (0.1324) \\ \hline
\end{tabular}
\label{tab:CTP} 
\end{table} 
\begin{figure}[h]
  \caption{CTP Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{CTP_QM.png}  
  \label{fig:CTP_QM}
\end{figure}

\noindent The mean values for coverage difference are exactly the same for both algorithms. In fact a paired t-test also shows the means are not statistically difference(p>0.05). For Pareto spread, MATLAB's MOGA performs the highest.

\section{Robust Problems} 
Some discussion of the robust methods here.

@@

\noindent Figure~\ref{fig:robust} shows a sample result from both MATLABs built in MOGA and the robust MOGA developed in this project. Table~\ref{tab:robustTNK} summarizes the mean quality metrics for each algorithm for ten runs.
\begin{figure}[h]
  \caption{Example Pareto Results for TNK}
  \centering
  \includegraphics[width=0.85\textwidth]{prob7_nChr25_nRun400.png}  
  \label{fig:robustTNK}
\end{figure}

\begin{table}[h]
\caption{Quality Metrics for Robust TNK (10 Runs)} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric &  Our MOGA \\ \hline
CD & 0.95 (0.014) \\ \hline
OS & 0.66 (0.012) \\ \hline
\end{tabular}
\label{tab:robustTNK} 
\end{table}

@@

\noindent The function $flightTime(\textbf{x},\textbf{y})$ is a black-box. The values $\textbf{xc}_j$ and  $\textbf{yc}_j$ specify the exclusion zone centers while $\textbf{r}_j$ specify the radii. A solution to this problem is shown in figure \ref{fig:FPP}.  In this figure there are two exclusion zones.
\begin{figure}[h]
  \caption{True Pareto Frontier for CTP}
  \centering
  \includegraphics[width=0.85\textwidth]{FPP.png}  
  \label{fig:FPP}
\end{figure}

\begin{figure}[h]
  \caption{True Pareto Frontier for CTP}
  \centering
  \includegraphics[width=0.85\textwidth]{FPP_pareto.png}  
  \label{fig:FPP_pareto}
\end{figure}

 \newpage
\vspace{-0.1in}
\bibliographystyle{IEEEtran}
\bibliography{references.bib}

>>>>

\usepackage{color} %red, green, blue, yellow, cyan, magenta, black, white
\definecolor{mygreen}{RGB}{28,172,0} % color values Red, Green, Blue
\definecolor{mylilas}{RGB}{170,55,241}
\usepackage{float}
\floatplacement{figure}{H}

\usepackage{caption}

@@

\noindent The next sections shall discuss the unconstrained problems ZDT1, ZDT2, and ZDT3, the results from the fitness function NSGA and MATLAB's "ga" function as well as the results from MATLAB's "gamultiobj" function for each. 
\newpage
\subsection{ZDT1} 
The first test problem, denoted as ZDT1 in \cite{deb2001multi} is shown below.

@@

\noindent The true Pareto frontier for this problem occurs when $x_i = 0$ for i = 2,...,30. Figure~\ref{fig:ZDT1} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. The quality metrics chosen to evaluate this problem are Coverage Difference (CD)and Pareto Spread (OS). Ten runs for each algorithm were performed and the mean and standard deviation of each metric are tabulated in Table~\ref{tab:ZDT1}.

\begin{figure}[h]
  \caption{Example Pareto Results for ZDT1}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT1_pareto_final.png}  
  \label{fig:ZDT1}
\end{figure}

@@

\newpage
\subsection{ZDT2} 
The second test problem, denoted as ZDT2 in \cite{deb2001multi} is shown below.

@@

\noindent The true Pareto frontier for this problem, similar to ZDT1, occurs when $x_i$ = 0 for i = 2,...,30. Figure~\ref{fig:ZDT2} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. Table~\ref{tab:ZDT2} summarizes the mean quality metrics for each algorithm for ten runs.
\begin{figure}[H]
  \caption{Example Pareto Results for ZDT2}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT2_pareto_final.png}  
  \label{fig:ZDT2}
\end{figure}

\begin{table}[H]
\caption{Quality Metrics for ZDT2} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.7832  (0.0821) & 0.6971  (0.0094) \\ \hline
OS &  0.8781 (0.0946) & 1.0086 (0.0278)  \\ \hline
\end{tabular}
\label{tab:ZDT2} 
\end{table}
\begin{figure}[H]
  \caption{ZDT2 Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT2_QM.png}  
  \label{fig:ZDT2_QM}
\end{figure}
\newpage
\newpage
\newpage
\goodbreak
\newpage

\goodbreak

\newpage
\goodbreak
\subsection{ZDT3} 
The third test problem, denoted as ZDT3 in \cite{deb2001multi} is shown below.

@@

\begin{figure}[H]
  \caption{Example Pareto Results for ZDT3}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT3_pareto_final.png}  
  \label{fig:ZDT3}
\end{figure}

\begin{table}[H]
\caption{Quality Metrics for ZDT3} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.7407 (0.0050) & 0.7554 (0.0031) \\ \hline
OS & 0.8565 (0.0098) & 0.8489 (0.0180) \\ \hline
\end{tabular}
\label{tab:ZDT3} 
\end{table}
\begin{figure}[h]
  \caption{ZDT3 Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT3_QM.png}  
  \label{fig:ZDT3_QM}
\end{figure}

@@

\begin{align*}
\textrm{Minimize} ~~~~~ f_1(\textbf{x}) &= -(25(x_1-2)^2+(x_2-2)^2+(x_3-1)^2+(x_4-4)^2+(x_5-1)^2) \\
\textrm{Minimize} ~~~~~ f_2(\textbf{x}) &= \sum_{i=1}^{6}x_i^2 \\
\textrm{Subject to} ~~~~ g_1(x) &= 1-\frac{x_1+x_2}{2} \leq 0 \\
g_2(x) &= \frac{x_1+x_2}{6}-1 \leq 0 \\
g_3(x) &= \frac{x_2-x_1}{2}-1 \leq 0 \\
g_4(x) &= \frac{x_1-3x_2}{2}-1 \leq 0 \\
g_5(x) &= \frac{(x_3-3)^2+x_4}{4}-1 \leq 0 \\
g_6(x) &= 1-\frac{(x_5-3)^2+x_6}{4} \leq 0 \\
0 &\leq  x_1,x_2,x_6  \leq 10 \\
1 &\leq  x_3,x_5  \leq 5 \\
0 &\leq  x_4  \leq 6 \\
\end{align*}
\begin{figure}[H]
  \caption{True Pareto Frontier for OSY}
  \centering
  \includegraphics[width=0.85\textwidth]{OSY_pareto_true.png}  
  \label{fig:OSY_true}
\end{figure}

@@

\begin{table}[H]
\caption{Quality Metrics for OSY} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.7882 (0.1995) & 0.5507 (0.0685)  \\ \hline
OS & 0.5322 (0.3393) & 0.9608 (0.2427) \\ \hline
\end{tabular}
\label{tab:OSY} 
\end{table}
\begin{figure}[H]
  \caption{OSY Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{OSY_QM.png}  
  \label{fig:OSY_QM}
\end{figure}
\newpage
\subsection{TNK} 
This test problem, denoted as TNK in \cite{deb2001multi} is shown below with the true Pareto frontier shown in Figure~\ref{fig:TNK_true}.

\begin{align*}
\textrm{Minimize} ~~~~~ f_1(\textbf{x}) &= x_1 \\
\textrm{Minimize} ~~~~~ f_2(\textbf{x}) &= x_2 \\
\textrm{Subject to} ~~~~ g_1(x) &= -x_1^2-x_2^2+1+0.1\cos(16\arctan(\frac{x_1}{x_2})) \leq 0 \\
g_2(x) &= (x_1 - 0.5)^2 + (x_2 - 0.5)^2 -0.5 \leq 0 \\
0 &\leq  x_1,x_2 \leq \pi \\
\end{align*}
\begin{figure}[H]
  \caption{True Pareto Frontier for TNK}
  \centering
  \includegraphics[width=0.85\textwidth]{TNK_pareto_true.png}  
  \label{fig:TNK_true}
\end{figure}

@@

\begin{table}[H]
\caption{Quality Metrics for TNK} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD &  0.8581 (0.0480) & 0.7792 (0.0036) \\ \hline
OS & 0.4177 (0.3216) & 0.9763 (0.0178)\\ \hline
\end{tabular}
\label{tab:TNK} 
\end{table}
\begin{figure}[H]
  \caption{TNK Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{TNK_QM.png}  
  \label{fig:TNK_QM}
\end{figure}

\noindent Comparing the estimated Pareto frontiers to the true Pareto frontier, is is clear that our MOGA outperforms MATLAB's MOGA. The Pareto spread in our MOGA is significantly higher however the coverage difference is higher in MATLABs MOGA (p<0.05).
\newpage
\subsection{CTP} 
This test problem, denoted as CTP in \cite{deb2001multi} is shown below and the true Pareto frontier is shown in Figure~\ref{fig:CTP_true}.

\begin{align*}
\textrm{Minimize} ~~~~~ f_1(\textbf{x}) &= x_1 \\
\textrm{Minimize} ~~~~~ f_2(\textbf{x}) &= g(x)(1-\sqrt{\frac{f_1(x)}{g(x)}} \\
\textrm{Subject to} ~~~~ g_1(x) &= a|\sin(b\pi(\sin(\theta)(f_2(x)-e)+\cos(\theta)f_1(x))^c)|^d \\
&- \cos(\theta)(f_2(x)-e)-\sin(\theta)f_1(x) \leq 0 \\
\textrm{where} ~~~~~~~~~~ \theta &= -0.2\pi, a = 0.2, b=10, c=1, d=6, e = 1 \\
g(x) &= |1+(\sum_{i=2}^{10}x_i)^{0.25}| \\
0 &\leq  x_1  \leq 1 \\
-5 &\leq  x_i  \leq 5, i = 2,...,10 \\
\end{align*}
\begin{figure}[H]
  \caption{True Pareto Frontier for CTP}
  \centering
  \includegraphics[width=0.85\textwidth]{CTP_pareto_true.png}  
  \label{fig:CTP_true}
\end{figure}

@@

\begin{table}[H]
\caption{Quality Metrics for CTP} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.6802 (0.0067) &  0.6802 (0.0092) \\ \hline
OS & 0.7901 (0.0734) & 0.5959 (0.1324) \\ \hline
\end{tabular}
\label{tab:CTP} 
\end{table} 
\begin{figure}[H]
  \caption{CTP Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{CTP_QM.png}  
  \label{fig:CTP_QM}
\end{figure}

\noindent The mean values for coverage difference are exactly the same for both algorithms. In fact a paired t-test also shows the means are not statistically difference(p>0.05). For Pareto spread, MATLAB's MOGA performs the highest.
\newpage
\section{Robust Problems} 
To solve problems with an uncertain variable we implement RMOGA.  One way to ensure robustness for a given population considered in GA, is by finding the value of the uncertain variable which maximizes the constraint values acording to each member in the population.  Another way is to discretize the dependent variable and then find which uncertain variable in this set maximizes the constraint values.  This latter method is the one we chose because of the decreased execution time over the former.  These two options are shown in figure \ref{fig:discretize}.
   Since the uncertainty term only appears in the constraints portion of both of the problems we consider this discretization is fairly simple.  In addition, since the uncertain terms are linearly combined in the constraints, this discretization is trivial.

\begin{figure}[H]
  \caption{Options for making optimization robust to uncertain variables. }
  \centering
  \includegraphics[width=0.85\textwidth]{Robustness.png}  
  \label{fig:discretize}
\end{figure}

@@

\noindent Figure~\ref{fig:robust} shows a sample result from both MATLABs built in MOGA and the robust MOGA developed in this project. Table~\ref{tab:robustTNK} summarizes the mean quality metrics for each algorithm for ten runs.
\begin{figure}[H]
  \caption{Example Pareto Results for TNK}
  \centering
  \includegraphics[width=0.85\textwidth]{prob7_nChr25_nRun400.png}  
  \label{fig:robustTNK}
\end{figure}

\begin{table}[H]
\caption{Quality Metrics for Robust TNK (10 Runs)} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric &  Our MOGA \\ \hline
CD & 0.95 (0.014) \\ \hline
OS & 0.66 (0.012) \\ \hline
\end{tabular}
\label{tab:robustTNK} 
\end{table}

@@

\noindent The function $flightTime(\textbf{x},\textbf{y})$ is a black-box. The values $\textbf{xc}_j$ and  $\textbf{yc}_j$ specify the exclusion zone centers while $\textbf{r}_j$ specify the radii. A solution to this problem is shown in figure \ref{fig:FPP}.  In this figure there are two exclusion zones.
\begin{figure}[H]
  \caption{True Pareto Frontier for CTP}
  \centering
  \includegraphics[width=0.85\textwidth]{FPP.png}  
  \label{fig:FPP}
\end{figure}

\begin{figure}[H]
  \caption{True Pareto Frontier for CTP}
  \centering
  \includegraphics[width=0.85\textwidth]{FPP_pareto.png}  
  \label{fig:FPP_pareto}
\end{figure}

\begin{table}[H]
\caption{Quality Metrics for Robust FPP (10 Runs)} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric &  Our MOGA \\ \hline
CD & 0.2427 (0.0704) \\ \hline
OS & 0.4794 (0.1220) \\ \hline
\end{tabular}
\label{tab:robustTNK} 
\end{table}

%
%\begin{table}[h]
%\caption{Quality Metrics for Robust FPP with waypoint constraints(10 Runs)} 
%\centering 
%\begin{tabular}{|c|c|c|} 
%\hline\hline  
%Metric &  Our MOGA \\ \hline
%CD & 0.27 0.0269) \\ \hline
%OS & 0.4794 (0.1220) \\ \hline
%\end{tabular}
%\label{tab:robustTNK} 
%\end{table}

\vspace{-0.1in}
\bibliographystyle{IEEEtran}
\bibliography{references.bib}
